---
title: "changepoint_analysis"
output: html_document
---

This script does change point analysis of the novelty of keyword usage and on 4 descriptive statistics.

# Setup
```{r setup}
pacman::p_load(tidyverse, lubridate, changepoint, patchwork, here, ggridges, gridExtra, grid, gghighlight)

source(here("r_src", "r_utils", "change_point_detection.R"))

theme_set(theme_minimal(base_size = 14))

# make directories
make_dir <- function(dir){
  if (!dir.exists(dir)){
    dir.create(dir)
  }
}
dirs = c(here("figs"), here("supplementary"))
map(dirs, make_dir)

```

# Novelty analysis

## Load data locally
```{r load_data_locally}
df <- read_csv(here("data", "entropy_prop.csv")) %>% 
  mutate(min_counts = as.factor(min_counts),
         month = as.factor(quarter),
         min_occurences = as.factor(min_occurences),
         year = as.factor(year),
         window_size = as.factor(window_size),
         f_category = recode(f_category, aggregate = "Aggregate", Objektiv_beskrivelse = "Objective description")) %>% 
  group_by(f_category) %>% 
  arrange(date) %>% 
  ungroup()
```


## Translate the keywords that will be plotted
```{r}
df <- df %>% 
  rename(
    # F2
    `Delusional perception` = `primær vrangsansning`,
    `Catotonic` = `kataton*`,
    `3rd person` = `tredjepersons`,
    `2nd person` = `andenpersons`,
    Scenic = sceniske,
    Divine = guddommelig,
    `Delusional mood` = vrangstemning,
    Hypnogogic = hypnagoge,
    Occult = okkult,
    `Replaced control of affect` = `påførte følelser`,
    # F3
    `Nihilistic delusions` = `nihilistiske forestillinger`,
    Dysthymia = dysthymi,
    `Grandiose delusions` = `grandiose vrangforestillinger`,
    `Somatic syndrome` = melankoliform,
    `Delusions of guilt` = skyldsforestillinger,
    Reckless = hensynsløs,
    Overoptimism = `over-optimisme`,
    Overconfident = overmodig,
    `Unusual skills` = `usædvanlige evner`,
    `The end of the world` = `verdens undergang`,
    `Famous` = berømt,
    Cyclothymia = cyklothymi)
```


## Exploration
### Checking mean proportion of keywords
```{r mean_proportion_per_keyword}
mean_percent_proportion <- df %>% 
  filter(f_category == "Aggregate", window_size=="2") %>% 
  select_if(~!any(is.na(.))) %>% 
  select(-c(year, nsigma, tsigma, rsigma, quarter, novelty, resonance, transience)) %>% 
  summarise(across(where(is.numeric), mean)) %>%  
  gather() %>% 
  mutate(value = value*100) %>% 
  arrange(desc(value)) 
  
mp_hist <- mean_percent_proportion %>% 
  ggplot(aes(value)) +
  geom_histogram() +
  labs(x = "", y = "Count")


mp_box <- mean_percent_proportion %>% 
  ggplot(aes(value)) +
  geom_boxplot() +
  labs(y ="", x = "Mean % of all keywords")

mp_plot <- mp_hist / mp_box + plot_layout(nrow = 2, height = c(2, 1))
mp_plot

ggsave(here("supplementary", "mean_percent_per_keyword.png"), dpi="retina", width = 10, height = 8, bg = "#ffffff")
ggsave(here("supplementary", "mean_percent_per_keyword.tiff"), dpi="retina", width = 10, height = 8, bg = "#ffffff")


format(summary(mean_percent_proportion$value), scientific = F)

```

Fairly long tailed distribution of word usage. The median value for how large a percentage of all words each word makes up is 0.05 (out of 305 word, so if all words were used evenly the value would be ~0.33%)


### See development for each keyword
```{r individual_keyword_development, eval=FALSE}
date_keyword_percentages <- df %>% 
  filter(f_category == "Aggregate", window_size=="2") %>% 
  dplyr::select((where(is.numeric)), date) %>% 
  select(-c(nsigma, tsigma, rsigma, quarter, novelty, resonance, transience)) %>%
  mutate(date = as.yearqtr(date, format = "%Y-%m-%d")) %>% 
  pivot_longer(-date) %>% 
  mutate(value = value * 100) %>% 
  # remove last quarter as it is incomplete
  filter(date < "2020 Q4")

for(keyword in unique(date_keyword_percentages$name)){
  p <- date_keyword_percentages[date_keyword_percentages$name == keyword,] %>% 
    ggplot(aes(x = date, y = value)) +
    geom_line() +
    labs(title = keyword)
  filename <-  paste0(plot_dir, "/keyword_development/", keyword, "_development.png")
  
  ggsave(filename, p)
}

```


### Robustness of novelty across different window sizes
```{r novelty_robustness}

window_ps <- list()
for(i in unique(df$window_size)){
  sub <- df %>% 
    filter(f_category == "Aggregate", window_size == i)
  p <- estimate_and_plot_changepoints(x=sub$novelty, 
                                   time=sub$date, 
                                   window_size=i, 
                                   do_detrending = TRUE,
                                   detrend_method = "difference" 
                                   ) +
    labs(title = as.character(i)) +
    scale_x_date(date_breaks = "2 years", date_labels = "%Y")

  window_ps[[as.character(i)]] <- p
}
wrap_plots(window_ps)
```

Going with 2 quarters - no reason to think the dependencies are longer


### Check detrending methods
### Compare all methods
```{r detrending_methods_comparison}
WINDOW_SIZE <- 2

df_for_window_size_2 <- df %>% 
  filter(window_size == WINDOW_SIZE)


## Check which detrending method to use
detrended_ps <- list()
for(category in unique(df$f_category)){
  sub <- df_for_window_size_2 %>% 
    filter(f_category == category)
  p <- plot_detrended_ts(x = sub$novelty,
                         time = sub$date,
                         window_size = WINDOW_SIZE,
                         detrending_method = "all",
                         do_smoothing = TRUE,
                         smoothing_span=0.75,
                         n_knots=4,
                         lag=1) +
    labs(title = category, y = "", x = "") +
    theme(axis.title = element_blank()) +
    scale_x_date(date_breaks = "2 years", date_labels = "%Y")

  detrended_ps[[category]] <- p
  
}
detrended_ps <- wrap_plots(detrended_ps)

# adds a joint x and y axis to a wrapped_plot grob
prettify_wrapped_plots <- function(p, left, bottom, fontsize=16){
  p <- patchworkGrob(p)
  p <- gridExtra::arrangeGrob(p, left=left, bottom=bottom)
  p$gp <- gpar(fontsize=fontsize)
  return(p)
}

detrended_ps <- prettify_wrapped_plots(detrended_ps, left="Novelty", bottom="Year")
plot(detrended_ps)

ggsave(here("supplementary", "detrending_methods.png"), plot=detrended_ps, dpi="retina", width = 10, height = 8, bg = "#ffffff")
ggsave(here("supplementary", "detrending_methods.tiff"), plot=detrended_ps, dpi="retina", width = 10, height = 8, bg = "#ffffff")


plot_detrended_groups(df_for_window_size_2, novelty, date, f_category, do_scale=F, highlight_above_value=0.002, facet=F)
plot_detrended_groups(df_for_window_size_2, novelty, date, f_category, do_scale=T)



```

Differencing seems to remove almost all trend - going with that

### Compare differenced ts to original
```{r differenced_and_org_ts_comparison}
detrended_ps <- list()
for(category in unique(df$f_category)){
  sub <- df_for_window_size_2 %>% 
    filter(f_category == category)
  p <- plot_detrended_ts(x = sub$novelty,
                         time = sub$date,
                         window_size = WINDOW_SIZE,
                         detrending_method = "difference",
                         do_smoothing = TRUE,
                         smoothing_span=0.75,
                         n_knots=4,
                         lag=1) +
    labs(title = category, y = "", x = "") +
    theme(axis.title = element_blank()) +
    scale_x_date(date_breaks = "2 years", date_labels = "%Y")

  detrended_ps[[category]] <- p
  
}
differenced_ps <- wrap_plots(detrended_ps)
differenced_ps <- prettify_wrapped_plots(differenced_ps, left="Novelty", bottom="Year")
plot(differenced_ps)

ggsave(here("supplementary", "differenced_and_original_ts.png"), plot=differenced_ps, dpi="retina", width = 10, height = 8, bg = "#ffffff")
ggsave(here("supplementary", "differenced_and_original_ts.tiff"), plot=differenced_ps, dpi="retina", width = 10, height = 8, bg = "#ffffff")


```


## Change point detection

### Detrend and plot changepoints on original time series
```{r changepoints_on_org_ts}
DETREND_METHOD <- "difference"


non_keyword_cols <- c("year", "date", 
                      "novelty", "transience", "resonance", 
                      "nsigma","tsigma", "rsigma",
                      "window_size", "f_category",
                      "log_counts", "min_counts", "min_occurences",
                      "quarter",
                      "month")


ps <- list()
for(category in unique(df$f_category)){
  sub <- df_for_window_size_2 %>% 
    filter(f_category == category)
  n_keywords <- sub %>% 
    select(where(~ !any(is.na(.x)))) %>% 
    select(!non_keyword_cols) %>%
    ncol() 
  p <- estimate_and_plot_changepoints(x = sub$novelty, 
                                      time = sub$date,
                                      window_size = WINDOW_SIZE,
                                      do_detrending = TRUE,
                                      do_smoothing = FALSE,
                                      detrend_method = DETREND_METHOD,
                                      smoothing_span=0.75,
                                      cp_plot_type = "line", # or point
                                      lag=1) +
        labs(title = str_wrap(category, 15), subtitle = glue::glue("{n_keywords} words")) +
        theme(axis.title = element_blank()) +
        scale_x_date(date_labels = "%Y", breaks = as.Date(c("2014-01-01", "2017-01-01", "2020-01-01")))

  ps[[category]] <- p
  
}
ps <-wrap_plots(ps, ncol=3)
ps <- prettify_wrapped_plots(ps, left="Novelty", bottom="Year")
ps

plot(ps)

ggsave(here("figs", "changepoints_on_org_timeseries.png"), plot=ps, dpi="retina", width = 7, height = 10, bg="#ffffff")
ggsave(here("figs", "changepoints_on_org_timeseries.tiff"), plot=ps, dpi="retina", width = 7, height = 10, bg = "#ffffff")


```


### Plot only change points
```{r only_changepoints}

min_time <- min(df_for_window_size_2$date)
max_time <- max(df_for_window_size_2$date)

df_for_window_size_2 %>% 
  mutate(f_category = case_when(
    f_category == "F0" ~ "F0 - Organic disorders",
    f_category == "F1" ~ "F1 - Substance abuse",
    f_category == "F2" ~ "F2 - Psychotic disorders",
    f_category == "F3" ~ "F3 - Mood disorders",
    f_category == "F4" ~ "F4 - Neurotic & stress-related",
    f_category == "F5" ~ "F5 - Eating & sleeping disorders",
    f_category == "F6" ~ "F6 - Personality disorders",
    f_category == "F7" ~ "F7 - Mental retardation",
    f_category == "F8" ~ "F8 - Developmental disorders",
    f_category == "F9" ~ "F9 - Child & adolescent disorders",
    f_category == "Aggregate" ~ "Aggregated words",
    f_category == "Objective description" ~ "Mental state examination",
    TRUE ~ f_category
    )
    ) %>% 
  estimate_and_plot_changepoints_by_group(ts_col = novelty,
                                          time_col = date, 
                                          group_col = f_category, 
                                          window_size = WINDOW_SIZE,
                                          label_format="quarter",
                                          plot_no_cps=TRUE) +
  expand_limits(y = c(as.Date(min_time), as.Date(max_time))) +
  labs(y = "Date", x = "(Diagnostic) categories of words describing psychopathology")

ggsave(here("figs", "only_changepoints.png"), dpi="retina", width = 10, height = 10, bg = "#ffffff")
ggsave(here("figs", "only_changepoints.tiff"), dpi="retina", width = 10, height = 10, bg = "#ffffff")



```


## What happened in 2020 for F2 keywords?
The calculation of novelty is based on the JSD divergence between distributions. JSD/KLD is sensitive to changes in keyword proportions _relative_ to previous time steps. I.e. to identify which keywords drove the change in novelty, we should find those that have the largest relative change. 
### Functions for calculating and plotting relative change
```{r}

## calculate relative change
relative_change <- function(x, signed){
  stopifnot(length(x) == 2)
  rel_change <- x[1] / x[2]
  # make sure always same scale no matter if largest number first or last
  if(rel_change < 1){
    rel_change = rel_change^-1 
    if(isTRUE(signed)){
      rel_change <- rel_change * -1
    }
  }
  return(rel_change)
}


#' plot change in proportions
#` requires a sorted list of values with the largest change
plot_proportion_change <- function(df, 
                                   date_of_changepoint, 
                                   date_of_window_start, 
                                   start_date, 
                                   end_date, 
                                   largest_change,
                                   add_absolute_change=NULL
                                   ){
  
  largest_change_annotation <- largest_change %>% 
    mutate(label = paste0("\u03D8: ", round(dif, 2)),
           xpos = as.Date(start_date),
           ypos = Inf,
           hjustvar = -0.1,
           vjustvar = 1.3)
  # largest_change_names <- largest_change$name
  largest_change_names <- largest_change$name

  p <- df %>% 
    select(all_of(largest_change_names), date) %>% 
    pivot_longer(-date) %>% 
    mutate(cps = case_when(
      date == date_of_changepoint ~ "Changepoint",
      date < date_of_changepoint & date >= date_of_window_start ~ "Window",
      TRUE ~ "Outside window"
      ),
      cps = fct_relevel(cps, "Outside window", "Window", "Changepoint")
     ) %>% 
    ggplot(aes(date, value)) +
    geom_point(aes(color=cps)) +
    geom_smooth(se=FALSE, span=0.2, color="grey", alpha=0.2) +
    scale_color_manual(values=c("lightgrey", "steelblue", "firebrick")) +
    geom_text(data=largest_change_annotation, 
              aes(label=label, x=xpos, y=ypos, hjust=hjustvar, vjust=vjustvar)) +
    # zoom in a  bit
    coord_cartesian(xlim = c(start_date, end_date)) +
    theme(legend.position = "bottom",
          legend.title = element_blank()) +
    labs(x = "Date", y = "Proportion") 
  
  if(!is_null(add_absolute_change)){
    absolute_change_annotation <- add_absolute_change %>% 
      mutate(label = paste0("\u0394: ", round(absolute_change, 3)),
             xpos = as.Date(end_date),
             ypos = Inf,
             hjustvar = 1,
             vjustvar = 1.3)
    
    p <- p + geom_text(data=absolute_change_annotation,
                       aes(label=label, x=xpos, y=ypos, hjust=hjustvar, vjust=vjustvar))
  }
    
    # order by magnitude of change
    p +  
      facet_wrap(~factor(name, levels=largest_change_names), scales="free_y", nrow=4, ncol=3)
  
}



calculate_and_plot_largest_change <- function(df, 
                                date_of_interest, 
                                window_size, 
                                plot_window, 
                                change="relative",
                                n_columns=12,
                                signed=FALSE,
                                plot=TRUE,
                                add_absolute_change=TRUE){
  # Assumes dataframe with 'date' and n keyword columns
  # change can be absolute or relative
  all_dates = unique(df$date)
  date_idx <- which(all_dates == as.Date(date_of_interest))
  first_date_segment_idx <- date_idx - window_size
  
  # calculate indices for plotting
  plot_start_date_idx <-  date_idx - plot_window
  plot_end_date_idx <- date_idx + plot_window
  # to avoid indexing out of bounds
  first_date_segment_idx <- if (first_date_segment_idx < 1) 1 else first_date_segment_idx
  plot_start_date_idx <- if (plot_start_date_idx < 1) 1 else plot_start_date_idx
  plot_end_date_idx <- if (plot_end_date_idx > length(all_dates)) length(all_dates) else plot_end_date_idx
  
  # Calculating the mean novelty/value for the past window_size time points and the time of interest
  df_mean_change <- df %>% 
    select(-novelty) %>% 
    filter(date >= all_dates[first_date_segment_idx], date <= all_dates[date_idx]) %>% 
    pivot_longer(-date) %>% 
    mutate(before_cp = if_else(date < all_dates[date_idx], 1, 0)) %>% 
    group_by(name, before_cp) %>% 
    summarise(avg = mean(value))
  
  if (change == "relative"){
    largest_change <- df_mean_change %>%  
      summarise(dif = relative_change(avg, signed=signed), 
                absolute_change = diff(avg)) %>% 
      arrange(desc(abs(dif))) %>% 
      slice(1:n_columns) 
    
    absolute_change <- largest_change %>% 
      select(name, absolute_change) %>% 
      # need to multiply by -1 to get correct order
      mutate(absolute_change = absolute_change * -1)
    largest_change <- largest_change %>% 
      select(name, dif)
    
  }
  if (change == "absolute"){
    largest_change <- df_mean_change  %>% 
      summarise(dif = diff(avg)) %>% 
      mutate(dif = dif * -1)
      arrange(desc(abs(dif))) %>% 
      slice(1:n_columns) 
    absolute_change <- largest_change %>% 
      rename(absolute_change = dif)
  }
  add_absolute_change <- if (isTRUE(add_absolute_change)) absolute_change else NULL
  
  if(isTRUE(plot)){
    p <- plot_proportion_change(df, 
                           date_of_changepoint=all_dates[date_idx], 
                           date_of_window_start = all_dates[first_date_segment_idx],
                           start_date = all_dates[plot_start_date_idx],
                           end_date = all_dates[plot_end_date_idx],
                           largest_change = largest_change,
                           add_absolute_change = add_absolute_change)
    return(p)
  }
  else{
    out = list(df=df, 
               date_of_changepoint=all_dates[date_idx],
               date_of_window_start = all_dates[first_date_segment_idx],
               start_date = all_dates[plot_start_date_idx],
               end_date = all_dates[plot_end_date_idx],
               largest_change = largest_change,
               add_absolute_change=add_absolute_change)
    return(out)
  }
}



```

### What happened with F3 keywords in 2020?
```{r}
f3 <- df_for_window_size_2 %>% 
    filter(f_category == "F3")

proportion_to_percent <- function(x) {x*100}

remove_cols <- non_keyword_cols[!non_keyword_cols %in% c("date", "novelty")]

f3_keywords <- f3 %>% 
    dplyr::select(where(~ !any(is.na(.x)))) %>% 
    select(!all_of(remove_cols)) %>% 
    mutate(date = as.Date(date)) %>% 
    mutate(across(where(is.numeric), proportion_to_percent))


calculate_and_plot_largest_change(f3_keywords, "2020-04-01", 
                                  window_size=WINDOW_SIZE, 
                                  plot_window=5, 
                                  change="relative",
                                  signed=TRUE,
                                  n_columns=12) +
  labs(y = "Proportion (%)")

filename <-here("figs", "f3_keywords")
ggsave(paste0(filename, ".png"), dpi="retina", width = 7, height = 10, bg = "#ffffff")
ggsave(paste0(filename, ".tiff"), dpi="retina", width = 7, height = 10, bg = "#ffffff")
```

### Plot change in F3 keywords without time series
```{r}
f3_prop <- calculate_and_plot_largest_change(f3_keywords, "2020-04-01", 
                                  window_size=WINDOW_SIZE, 
                                  plot_window=5, 
                                  change="relative",
                                  n_columns=12,
                                  signed=TRUE,
                                  plot=FALSE)

f3_difference <- f3_prop$add_absolute_change

f3_prop$largest_change %>% 
  left_join(f3_difference) %>% 
  mutate(name = as.factor(name),
         name = fct_reorder(name, abs(dif)),
         is_negative = if_else(dif < 0, "Decrease", "Increase"),
         hjustvar = if_else(name == "Nihilistic delusions", 1.3, -0.2),
         label = paste0("\u0394: ", round(absolute_change, 3))) %>% 
  ggplot(aes(abs(dif), name, shape=fct_rev(is_negative))) +
  geom_point() +
  geom_text(aes(label=label, hjust=hjustvar), color=alpha("black", 0.7)) +
  scale_shape_manual(values=c(3, 16)) + 
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  labs(x="Quotient difference", y="Word describing psychopathology") +
  xlim(1, 3)


filename <-here("figs", "quotient_delta_only")
ggsave(paste0(filename, ".png"), dpi="retina", width = 7, height = 7)
ggsave(paste0(filename, ".tiff"), dpi="retina", width = 7, height = 7)
```



# Change point detection on descriptive stats

## Load data locally
```{r load_td_local}
library(corrplot)
td_df <- read_csv(here("data", "td_stats.csv"))

td_df <- td_df %>% 
  select(date, 
         n_tokens_mean, 
         n_tokens_se,
         automated_readability_index_mean,
         dependency_distance_mean_mean, 
         overskrift_,
         n_tokens_count) %>% 
  mutate(date = as.Date(date)) %>% 
# Translate overskrift_ to English
  mutate(overskrift_  = case_when(
    overskrift_ == "Aftaler, Psykiatri" ~ "Appointments, Psychiatry",
    overskrift_ == "Aktuelt socialt, Psykiatri" ~ "Current social function, Psychiatry",
    overskrift_ == "Aktuelt psykisk" ~ "Current mental state",
    overskrift_ == "Aktuelt somatisk, Psykiatri" ~ "Current somatic, Psychiatry",
    overskrift_ == "Journalnotat" ~ "Patient note",
    overskrift_ == "Konklusion" ~ "Conclusion",
    overskrift_ == "Kontaktårsag" ~ "Reason for contact",
    overskrift_ == "Medicin" ~ "Medication",
    overskrift_ == "Objektivt psykisk" ~ "Objective mental state",
    overskrift_ == "Objektivt, somatisk" ~ "Objective, somatic",
    overskrift_ == "Observation af patient, Psykiatri" ~ "Observation of patient, Psychiatry",
    overskrift_ == "Ordination" ~ "Prescription",
    overskrift_ == "Plan" ~ "Plan",
    overskrift_ == "Samtale med behandlingssigte" ~ "Conversation with treatment aim",
    overskrift_ == "Semistruktureret diagnostisk interview" ~ "Semi-structured diagnostic interview",
    overskrift_ == "Telefonkonsultation" ~ "Telephone consultation",
    overskrift_ == "Telefonnotat" ~ "Telephone note",
    overskrift_ == "Aggregate" ~ "Aggregate"
  ))
  
# split aggreagte to calculate proportions
td_df_no_agg <- td_df %>% 
  filter(overskrift_ != "Aggregate")

td_df_only_agg <- td_df %>% 
  filter(overskrift_ == "Aggregate")

agg_total <- td_df_no_agg %>% 
  select(date, overskrift_, n_tokens_count) %>% 
  group_by(date) %>% 
  summarise(total_tokens = sum(n_tokens_count)) 
# Calculate counts

td_df_no_agg <-  td_df_no_agg %>% 
  left_join(agg_total, by = "date") %>% 
  group_by(overskrift_, date) %>% 
  mutate(proportion = n_tokens_count / total_tokens * 100) 


td_df <- td_df_no_agg %>% 
  bind_rows(td_df_only_agg)

td_df_incl_bad_data <- td_df

td_df <- td_df %>% 
  filter(date >= "2013-01-01") 


```

## Plot only changepoints
```{r td_only_changepoints}
min_time <- min(td_df$date)
max_time <- max(td_df$date)


# N. tokens
n_token_cp <- td_df %>% 
  estimate_and_plot_changepoints_by_group(ts_col = n_tokens_mean,
                                          time_col = date, 
                                          group_col = overskrift_, 
                                          window_size = NULL,
                                          plot_no_cps = TRUE,
                                          return_df=T
  ) %>% 
  mutate(Metric = "Number of tokens")


# Dependency distance
dep_dist_cp <- td_df %>% 
  estimate_and_plot_changepoints_by_group(ts_col = dependency_distance_mean_mean,
                                          time_col = date, 
                                          group_col = overskrift_, 
                                          window_size = NULL,
                                          return_df=T
  ) %>% 
  mutate(Metric = "Dependency distance")


# ARI
readability_cp <- td_df %>% 
  estimate_and_plot_changepoints_by_group(ts_col = automated_readability_index_mean,
                                          time_col = date, 
                                          group_col = overskrift_, 
                                          window_size = NULL,
                                          return_df = T
  )  %>% 
  mutate(Metric = "ARI")


# Proportion
prop_cp <- td_df %>% 
  estimate_and_plot_changepoints_by_group(ts_col = proportion,
                                          time_col = date, 
                                          group_col = overskrift_, 
                                          window_size = NULL,
                                          return_df = T
  ) %>% 
  mutate(Metric = "Proportion")


all_cp <- bind_rows(n_token_cp, dep_dist_cp, readability_cp, prop_cp)



all_cp <- all_cp %>% 
  mutate(overskrift_ = as.factor(overskrift_))

all_cp %>% 
  mutate(overskrift_ = fct_rev(overskrift_)) %>% 
  ggplot(aes(overskrift_, date, color = Metric)) +
    geom_point(size = 3, shape = 17) + 
    geom_label_repel(aes(label = as.character(as.yearqtr(date)))) + # can add direction="x" to  only nudge on x axis
    expand_limits(y = c(min_time, max_time)) + 
    scale_x_discrete(labels = function(x) str_wrap(x, width=25)) +
    coord_flip() +
    labs(y = "Date", x = "Note type") +
    scale_color_brewer(palette="Set1") +
    theme(axis.text.y = element_text(size=14))

filename <-here("figs", "td_only_changepoints")
ggsave(paste0(filename, ".png"), dpi="retina", width = 10, height = 10, bg = "#ffffff")
ggsave(paste0(filename, ".tiff"), dpi="retina", width = 10, height = 10, bg = "#ffffff")
  
```

## Plot changepoints on each original time series for each category and note type
```{r td_changepoints_on_org_data}
theme_set(theme_minimal()) 

plot_feature <- function(column, y_lab){
  cp_plots <- list()
  for(category in sort(unique(td_df$overskrift_))){
    if(category == "Aggregate" & column == "proportion"){
      # Can't calculate proportion for aggregate so skipping it
      next
    }
    sub <- td_df %>% 
      filter(overskrift_ == category)
    p <- estimate_and_plot_changepoints(x = sub[[column]],
                                        time = sub$date,
                                        window_size = NULL,
                                        do_smoothing=FALSE
    ) +
      labs(title = str_wrap(category, 19), y = y_lab) +
      theme(axis.title = element_blank()) +
      scale_x_date(date_breaks = "2 years", date_labels = "%Y")
    cp_plots[[category]] <- p
    
  }
  return(cp_plots)
}

features <- c("n_tokens_mean", "dependency_distance_mean_mean", "automated_readability_index_mean", "proportion")
y_labs <- c("N. tokens", "Mean Dep. Dist", "ARI", "Proportion (%)")

plots <- map2(features, y_labs, plot_feature)

wrap_plots_3_cols <- function(plots){
  return(wrap_plots(plots, ncol=3))
}

ps <- map(plots, wrap_plots_3_cols)

new_ps <- list()
ii <- 1
for (p in ps){
  p <- prettify_wrapped_plots(p, left=y_labs[ii], bottom="Year")

  filename <- if(str_detect(y_labs[[ii]], "%")) "Proportion" else y_labs[[ii]]
  filename <- here("supplementary", glue::glue("{filename}_changepoints_on_org_timeseries_td"))
  
  ggsave(paste0(filename, ".png"), plot = p, dpi="retina", width = 7, height = 10, bg = "#ffffff")
  ggsave(paste0(filename, ".tiff"), plot= p, dpi="retina", width = 7, height = 10, bg = "#ffffff")
  new_ps[[y_labs[ii]]] <- p
  ii = ii + 1
}


```


## Plot detrended time series
```{r}
# scale before detrending
plot_detrended_groups(td_df, proportion, date, overskrift_, do_scale=T, facet=T)
plot_detrended_groups(td_df, automated_readability_index_mean, date, overskrift_, do_scale=T) 
plot_detrended_groups(td_df, n_tokens_mean, date, overskrift_, do_scale=T) 
plot_detrended_groups(td_df, dependency_distance_mean_mean, date, overskrift_, do_scale=T) 
```

## Visualize problematic data in 2011 and 2012
```{r}
theme_set(theme_minimal(base_size = 14))


p <- td_df_incl_bad_data %>% 
  select(date, n_tokens_mean, n_tokens_se) %>% 
  filter(overskrift_ == "Aggregate") %>% 
  ggplot(aes(x = date, y = n_tokens_mean)) +
  geom_errorbar(aes(ymin=n_tokens_mean - n_tokens_se, ymax=n_tokens_mean + n_tokens_se)) +
  geom_point(size=1) +
  labs(x="Date", y="N. tokens")
  
p

filename <- here("supplementary", "mean_tokens_incl_2011_2012")
ggsave(paste0(filename, ".png"), plot = p, dpi="retina", width = 6, height = 4, bg = "#ffffff")
```


## Visualise the aggregate metrics together
```{r}
# Novelty for aggregate
novelty_agg <- df_for_window_size_2 %>% 
  filter(f_category == "Aggregate") %>% 
  select(date, novelty) %>% 
  mutate(name = "Novelty") %>% 
  rename(value = novelty)

agg_df <- td_df %>% 
  ungroup() %>% 
  filter(overskrift_ == "Aggregate") %>% 
  select(date, n_tokens_mean, dependency_distance_mean_mean, automated_readability_index_mean) %>% 
  pivot_longer(-date) %>% 
  mutate(name = case_when(
    name == "n_tokens_mean" ~ "Number of tokens",
    name == "dependency_distance_mean_mean" ~ "Dependency distance",
    name == "automated_readability_index_mean" ~ "ARI"
  )) %>% 
  bind_rows(novelty_agg) 



agg_plots <- list()

for(var in sort(unique(agg_df$name))[c(1,2,4,3)]){
  sub <- agg_df %>% 
    filter(name == var)
  window_size = if (var == "Novelty") 2 else NULL
  p <- estimate_and_plot_changepoints(x = sub$value,
                                      time=sub$date,
                                      window_size=window_size,
                                      do_smoothing=FALSE
  ) +
    labs(y = var)  +
    theme(axis.title.x = element_blank())
    scale_x_date(date_breaks = "2 years", date_labels = "%Y")
  agg_plots[[var]] <- p
}

# add same plot but with y-axis going to zero
agg_plots_zero_y <- list()
i <- 1
for(plot in agg_plots){
  p <- plot +
    ylim(0, NA)
  agg_plots_zero_y[[paste0(unique(agg_df$name)[i], "_zero_y")]] <- p
  i = i + 1
}


agg_plots_zero_y <- wrap_plots(agg_plots_zero_y, ncol=1)
agg_plot <- wrap_plots(agg_plots, ncol=1)

agg_plot <- agg_plots_zero_y | agg_plot
agg_plot <- prettify_wrapped_plots(agg_plot, left=NULL, bottom="Year")

filename <- here("figs", "all_aggregate")
ggsave(paste0(filename, ".png"), plot = agg_plot, dpi="retina", width = 6, height = 8, bg = "#ffffff")

```


